\name{}: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-04-09 paper/main.tex
.

\subsubsection{Metrics}
\label{sec:evaluation}
To assess each model, we compute a variety of common metrics for
binary classification. As the datasets are highly imbalanced, we use
the area under the receiver operating characteristic curve
(AUROC) on training, validation and testing split. % We
% calculated the true positive rate (TPR), false positive rate (FPR), and
% precision score. We will further compute true positives (TP), false
% positives (FP), false negatives (FN) and finally true negatives (TN).

@@

\todo[inline]{For RH: check this again later:}
We also calculate the $\textrm{MicroAUC}$ score. For given lists $D$
and $P$ of drugs and proteins, respectively, and a set of known
interactions $Int := \{(d_i, p_i) \}$, \textit{MicroAUC} is calculated
as the average per entity (macro) \textit{AUROC} score. Specifically,
for protein-centric score, this can be formalized as: given labels
$l:D\times P \rightarrow \{0,1\}$ and predictions $y:D\times P
\rightarrow [0,1]$, we define
\begin{equation*}
  \textrm{MicroAUC}'_p(l,y) := \underset{p\in P}{mean}\left(\left\{
      \text{AUROC}(\{ (l(d_i, p), y(d_i,p))| d_i\in D\})
    \right\}\right)
\end{equation*}

In some cases, the $MicroAUC'$ score may not be defined as in some
datasets some proteins or drugs have no interactions, leading to an
infeasible $TPR=0$ for all thresholds and an undefined $AUROC$ score
for that entity. For those entities, we impute the $MicroAUC$
interpolating linearly, by using the accuracy for this
subset:

\begin{equation*}
	\textrm{MicroAUC}_p(l,y) := 
	\begin{cases}
		MicroAUC'_p(l,y) & \text{if }\sum_{d_i\in D}l(d_i,p)\neq0\\
		Accuracy(l,y)&otherwise
	\end{cases}
\end{equation*}

Note that drugs and proteins can be interchanged in this formulation. We
refer to the different measures as protein-centric microAUC
($MicroAUC_p$) and a drug-centric microAUC ($MicroAUC_d$).

>>>>

\subsubsection{Metrics}
\label{sec:evaluation}
To assess each model, we compute a variety of common metrics for
binary classification. As the datasets are highly imbalanced, we use
the area under the receiver operating characteristic curve
(AUROC) on training, validation and testing split.
% We calculated the true positive rate (TPR), false positive rate
% (FPR), and precision score. We will further compute true positives
% (TP), false positives (FP), false negatives (FN) and finally true
% negatives (TN).

@@

We also calculate the $\textrm{MicroAUC}$ score. For given lists $D$
and $P$ of drugs and proteins, respectively, and a set of known
interactions $Int := \{(d_i, p_i) \}$, \textit{MicroAUC} is calculated
as the average per entity \textit{AUROC} score. For example, the
protein-centric score can be formalized as: given labels
$l:D\times P \rightarrow \{0,1\}$ and predictions
$y:D\times P \rightarrow [0,1]$, we define
\begin{equation*}
  \textrm{MicroAUC}'_p(l,y) := \underset{p\in P}{mean}\left(\left\{
      \text{AUROC}(\{ (l(d_i, p), y(d_i,p))| d_i\in D\})
    \right\}\right)
\end{equation*}

In some cases, the $MicroAUC$ score may not be defined as in some
datasets some proteins or drugs have no interactions, leading to an
infeasible $TPR=0$ for all thresholds and an undefined $AUROC$ score
for that entity. For those entities, we impute the $MicroAUC$
interpolating linearly, by using the accuracy for this
subset:
\begin{equation*}
	\textrm{MicroAUC}_p(l,y) := 
	\begin{cases}
		MicroAUC'_p(l,y) & \text{if }\sum_{d_i\in
                  D}l(d_i,p)\neq 0\\
		Accuracy(l,y)&otherwise
	\end{cases}
\end{equation*}
Drugs and proteins can be interchanged in this formulation. We refer
to the different measures as protein-centric microAUC ($MicroAUC_p$)
and a drug-centric microAUC ($MicroAUC_d$).
